Effects of gluon kinematics and the Sudakov form factor on the GBW and BGK saturation models

### 2023-04-24 Paper/draft.tex
domument update

\begin{abstract}
We investigate effects of exact gluon kinematics on the parameters of the
Golec-Biernat--W\"sthoff, and Bartels--Golec-Biernat--Kowalski models. The
resulting parameters show sizable difference, particularly in the normalization
$\sigma_0$. The resulting models are applied for the dijet process in DIS to
investigate effects of the Sudakov form factor.  The result qualitatively agrees
with that of Ref.~\cite{vanHameren:2021sqc}, except for the difference stemming
from the large-$k_T$ behaviour of the models.
\end{abstract}

@@

  \draw[ snake=coil,segment aspect=1.5,segment length=0.1in](0.5in , -1in)--(0.5in,-0.5in);
  \draw[snake=coil,segment aspect=1.5,segment length=0.1in](-0.5in , -1in)--(-0.5in,-0.5in);
\end{tikzpicture}
}
\caption{Kinematic variables of the gluon contribution to $F_2$. The momentum fraction of gluon is $x/z$ as it has to contribute via the quark box.
}
\label{fig:gluon-kinem}
\end{figure}
%Factorization has played central role in QCD, where one expresses a cross section in terms of factors, each depends on a different scale. Parton Distribution Functions (PDF) are examples of such objects which appear in factorization. The PDFs describe the structure of hadrons, and they are process independent. As PDFs are not perturbatively calculable objects, they have to be obtained from experiments. 
%Deeply Inelastic Scattering (DIS) is one of such experiments which can probe the structure of proton. Process independence means that the PDFs obtained in DIS can be used in other experiments such as proton-proton collision.

In the small-$x$ region of deep intelastic scattering (DIS) process   
%
\begin{equation}
  %\label{eq:}
  e\, p\rightarrow \gamma^* (q)\, p(p)\rightarrow X\,,
\end{equation}
%
where are $p$ and $q$ are, respectively, the momenta of the photon and the
proton, the interactions are dominated by gluons\cite{Kovchegov:2012mbw}. As a photon does not interact directly with a gluon, it interact through a box of quarks as depicted in Fig.~\ref{fig:gluon-kinem}. 
An object, which is central to the description of this process is called dipole gluon density, $\mathcal{F}(x,k_T^2)$, which is a type of transverse momentum dependent PDFs (TMD PDF)~\cite{Dominguez:2010xd,Dominguez:2011wm,Xiao:2017yya}. This appears in the $k_T$-factorization formula~\cite{Dominguez:2010xd,Dominguez:2011wm,Xiao:2017yya}, which we will discuss later, and plays role similar to that of collinear parton distribution function in the collinear factorization.
The dipole gluon density is also called unintegrated gluon density~(UGD) since it is related to the collinear (integrated) gluon density by
\begin{equation}
xg(x,Q^2)=\int^{Q^2}_0 dk_T^2 \mathcal{F}(x,k^2_t).
\end{equation}
Much effort has been made to study this object, notably the work of Balistky, Fadin, Kuraev and Lipatov (BFKL)~\cite{Balitsky:1978ic, Kuraev:1977fs} has predicted sharp rise of cross sections with $1/x$.  However, such rise violates unitarity and the Froissart bound~\cite{Kovchegov:2012mbw,Barone:1993sy}. The work of Balitsky and Kovchegov (BK)~\cite{Balitsky:1995ub,Kovchegov:1999yj} incorporated the gluon recombination, by including nonlinear term in the evolution, thus taming the growth. The phenomenon described by this nonlinear term is called saturation. The meaning of the Froissart bound is that, asymptotically, the cross section can not grow faster than the size of black-disk (proton with high gluon density) which expands like $\ln(s)$~\cite{Badelek:1992gs}.
Despite the success of such evolution equations, there are several popular phenomenological models owing to their simplicity.

\comment{Some more general talk like in the previous paper}

\comment{EIC}

@@

Additionally, let us introduce $q'\equiv q+x p$. 
Then, one  decomposes $k$ and $\kappa$ (Fig.~\ref{fig:gluon-kinem}) as
\begin{align}
    \kappa&=\alpha p-\beta q'+\kappa_t&&\mathrm{and}& k&=a p- bq'+k_T.
\end{align}
For the contribution depicted in Fig.~\ref{fig:gluon-kinem}, the structure function, $F_2$ for transversely and longitudinally polarized photons, factorize, with a change of variable  ${\boldsymbol{\kappa}'}_t\equiv{\boldsymbol{\kappa}_t}-(1-\beta)\mathbf{k}_t$, in the form~\cite{ Kimber:2001uaa,Kwiecinski:1997ee}
\begin{multline}
	F_2(x,Q^2)=\sum_f e_f^2 \frac{Q^2}{2\pi}\int\frac{dk^2_t}{k_T^2}\int^1_0d\beta\int d{\kappa'}_t\alpha_s(\mu^2) \mathcal{F}(x/z,k_T^2)\Theta(1-x/z)\\
	\left[\left(\beta^2+(1-\beta)^2\right)\left(\frac{I_1}{2\pi}-\frac{I_2}{2\pi}\right)
	+\left(m_f^2+4Q^2\beta^2(1-\beta)^2\right)\left(\frac{I_3}{2\pi}-\frac{I_4}{2\pi}\right)\right],
	\label{eq:angle-integrated}
\end{multline}
where
\begin{equation}
	\frac{1}{z}=1+\frac{{\kappa'}^2_t+m_f^2}{\beta(1-\beta)Q^2}+\frac{k^2_t}{Q^2}.
	\label{eq:z}
\end{equation}
(see Ref.~\cite{ Kimber:2001uaa,Kwiecinski:1997ee} for detail.)
%and
%\begin{equation}
%	\begin{split}
%		\frac{I_1}{2\pi}=\frac{N_1N_2+N_3^2}{\left( N^2_1+2N_1N_2+N_3^2\right)^{3/2}}, &\hspace{1cm}
%		\frac{I_2}{2\pi}=\frac{N_3-(1-2\beta)N_1}{(N_1+N_4)\sqrt{ N^2_1+2N_1N_2+N_3^2}},\\
%		\frac{I_3}{2\pi}=\frac{N_1+N_2}{\left( N^2_1+2N_1N_2+N_3^2\right)^{3/2}},&\hspace{1cm}
%		\frac{I_2}{2\pi}=\frac{(1-\beta)}{(N_1+N_4)\sqrt{ N^2_1+2N_1N_2+N_3^2}},
%	\end{split}
%\end{equation}
%for
%\begin{equation}
%	\begin{split}
%		N_1\equiv\beta(1-\beta)Q^2+m_f^2, &\hspace{2cm}
%		N_2\equiv{\kappa'}_t^2+(1-\beta)^2k_T^2,\\
%		N_3\equiv{\kappa'}_t^2-(1-\beta)^2k_T^2, &\hspace{2cm}
%		N_4\equiv{\kappa'}_t^2+\beta(1-\beta)k_T^2.
%	\end{split}
%\end{equation}
%Hereafter, we will call Eq.~(\ref{eq:angle-integrated}) $k_T$-factorizaton formula.
One should note, that gluons are not probed directly, thus the argument of the gluon density is $x/z$ rather than $x$.
If one, instead, uses $ 1/z=\left(1+4 m_f^2/Q^2\right)$ and assumes that $\mu$ is independent of $\kappa'$ and $k_T$, 
the above formula can be written in the impact parameter space~\cite{Golec-Biernat:1998zce,Nikolaev:1990ja} (i.e. dipole-factorizaton formula)
\begin{equation}
F_2\left(x,Q^2\right)\sim\int^1_0d\beta \int d^2\mathbf{r}\left|\Psi\left(x,\beta,Q^2\right)\right|^2\sigma_{\mathrm{dipole}}\left(x,r\right),
\label{eq:dipole-factorization}
\end{equation}
where the photon wave function, $\left|\Psi\left(x,\beta,Q^2\right)\right|^2$, describes splitting of the incoming photon into a $q\overline{q}$ pair with light-cone momenta fractions $\beta$ and $1-\beta$ respectively, and the dipole cross section, $\sigma_{\mathrm{dipole}}\left(x,r\right)$, describes the interaction of the colour dipole of the size $r$ with the proton.\\

@@

The results of fits are summarized in Tab.~\ref{tab:table}. 
The fit quality of $k_T$-GBW is almost unchanged w.r.t. $r$-GBW, while the rc-$k_T$-GBW shows remarkable improvement, almost halving the $\chi^2$ value.
It was pointed out in Ref.~\cite{Albacete:2004gw,Albacete:2007yr,Albacete:2010sy} that in the BK evolution, the running coupling correction have considerable effects.
% \comment{What is the connection? Their result regarding the 1/x grad of $Q_s$ becoming smaller is clearly not present in our case. If we consider $\mathcal{F}$ with running coupling, it will be a bit bent in very small-x. besides, the analysis of \cite{Albacete:2004gw} extends to around $Y=\ln(x_0/x)\sim35$. for our case it may be just not low enough. (though around $Y=10$, $\alpha_0=0.2$ and running have sizable difference. ) }
Another notable point is that, except for the normalization $\sigma_0$, the parameters are very similar, particularly those of rc-$k_T$-GBW are almost identical to those of $r$-GBW. 
\comment{Describet what's in the figuers...}

\begin{figure}[p]
  \begin{multicols}{2}
    \includegraphics[width=0.49\textwidth]{./plots/GBW-dipole.pdf}
    \includegraphics[width=0.49\textwidth]{./plots/GBW-gluon.pdf}
    \includegraphics[width=0.49\textwidth]{./plots/GBW-saturation.pdf}\par
    \includegraphics[width=0.49\textwidth]{./plots/BGK-dipole.pdf}
    \includegraphics[width=0.49\textwidth]{./plots/BGK-gluon.pdf}
    \includegraphics[width=0.49\textwidth]{./plots/BGK-saturation.pdf}
  \end{multicols}
  \caption{The dipole cross section, the dipole gluon density at $x=10^{-2},\;
  10^{-6}$, and the saturation scale for the GBW (left) and the BGK (right)
  models Note, the dipole cross section and the gluon density are normalized by
  $\sigma_0^{-1}$. \sout{\comment{Larger y and x labels}}} 
\end{figure}

@@

\begin{figure}[p]
%\begin{subfigure}{\textwidth}
\includegraphics[width=0.49\textwidth]{./plots/Figure_2-1.png}
\includegraphics[width=0.49\textwidth]{./plots/Figure_2-2.png}
\includegraphics[width=\textwidth]{./plots/Figure_2-3.png}
%\end{subfigure}
\caption{Comparison of BGK $F_2$ with HERA data. The histogram shows the $\chi^2$ value per data point in each frame. While the overall fit quality remain similar, the fit quality in each frame change noticeably. Particularly the $k_T$-formula case ($k_T$) shows better fit in the small-$Q^2$ region.}
\label{fig:BGK-Grid}
\end{figure}

Let us analyze the difference in $\sigma_0$. 
Recalling that the difference between the $k_T$-factorization formula and the dipole-factorization formula is in $x/z$, where this enters in the GBW formalism as modified $x$. It is easy to see that, as $x$ grows, the dipole cross section gets suppressed (Keeping in mind the suppression by the photon wave function in the large-$r$ region.). Such effect was discussed previously in Ref.~\cite{Kutak:2004ym} in the context of the BK equation. In fact, this suppression is the motivation given in Ref.~\cite{Golec-Biernat:1998zce} for such modification of $x$, so that in the small-$Q^2$ limit, the total cross section remains finite.    
Since 
%
\begin{equation}
\left(1+\frac{4 m_f^2}{Q^2}\right)\leq\left(1+\frac{k_T^2}{Q^2}+\frac{{\kappa'}_t^2+m_f^2}{\beta(1-\beta)Q^2}\right),
\end{equation}
%
the $k_T$-factorization case receives more suppression. Consequently, the normalization factor $\sigma_0$ rises to compensate the suppression. Thus, one would expect that the massive light quarks partially simulate the effect of $x/z$.
It is therefore, interesting to see that the parameters of $k_T$-GBW, are closer to those of $r$-GBW-massive than to the parameters of $r$-GBW.    
However, it seems that there is a compensating factor in rc-$k_T$-GBW. 
The compensating effect can be understood as follows. As it is visible in  Fig.~\ref{fig:GBW}, larger $x_0$ enhances the small-$r$ region which corresponds roughly to the large-$k_T$ of the dipole gluon density which also is visible. 
As the running coupling depends on $k_T^2$,  one can expect that the large-$k_T$ region gets suppressed.  Therefore, one can conclude that the change in $x_0$ is a direct consequence of the running coupling.\\
While the GBW model remains almost unaffected, the BGK model seems to show slightly more change. The difference is more prominent in the small-$x$ region (Fig.~\ref{fig:BGK}), particularly noticeable in the second peak of the gluon density.
The change is cleanly visible in the saturation scale of Fig.~\ref{fig:BGK}. 
The resulting $F_2$ of respective models are shown in Figs.~\ref{fig:GBW-Grid}~and~\ref{fig:BGK-Grid}.

While the $r$-GBW and $k_T$-GBW show little difference, rc-$k_T$-GBW clearly shows better fit quality in the high-$Q^2$ region. This is clearly shown in the histogram at the bottom. 
As for the BGK model, the difference is too small to be seen in the top plots. However the bottom histogram shows some differences. While the small-$Q^2$ region is somewhat improved, as a whole, the changes cancel out.

%\begin{figure}[p]
%\center
%\includegraphics[width=0.9\textwidth]{../plots/dipole-GBW.png}\\
%\includegraphics[width=0.9\textwidth]{../plots/gluon-GBW.png}\\
%\includegraphics[width=0.9\textwidth]{../plots/gluon-GBW-contour.png}
%\caption{from left: r-BGK, kt-BGK}
%\end{figure}
%\begin{figure}[p]
%\center
%\includegraphics[width=0.9\textwidth]{../plots/dipole-BGK.png}\\
%\includegraphics[width=0.9\textwidth]{../plots/gluon-BGK.png}\\
%\includegraphics[width=0.9\textwidth]{../plots/gluon-BGK-contour.png}
%\caption{from left: r-BGK, kt-BGK}
%\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\section{Dijet process at EIC}
\label{Dijet process at EIC}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In order to investigate less inclusive processes, we will study the electron-dijet correlation at the electron-ion collider(EIC), following closely the method of Ref.~\cite{vanHameren:2021sqc}.

\comment{process}

\comment{factorization formula for dijets in DIS involving WW gluon}

\comment{mention why Sudakov is important for dijet production}

The dijet process is known to probe a type of unintegrated gluon density, called Weizs\"acker-Williams gluon density~\cite{Dominguez:2010xd,Dominguez:2011wm,Xiao:2017ggh}.
This UGD, $\fww(x,k^2)$, has an interpretation as a number density of gluons inside a proton~\cite{Dominguez:2010xd,Dominguez:2011wm,Dominguez:2011wm}. Under the Gaussian approximation and assuming $\theta$-like profile of the proton, one can write~\cite{vanHameren:2016ftb,Xiao:2017ggh,Dominguez:2010xd,Dominguez:2011wm}
\begin{equation}
\fww(x,k^2)= \frac{C_F}{2\pi^3\alpha_s}\int^\infty_0\frac{dr}{r}J_0(r k) \sdpa(x,r),
\end{equation} 	
with the adjoint dipole cross section
\begin{equation}
\sdpa(x,r)=\sigma_0\left( 1-\left(1-\frac{\sdp(x,r)}{\sigma_0}\right)^{C_A/C_F}\right).
\label{eq:ww}
\end{equation}
Resummation of the Sudakov logarithms is achieved by the formula~\cite{Mueller:2013wwa,Xiao:2017yya}
\begin{equation}
	\fww(x,k^2,\mu^2)= \frac{C_F}{2\pi^3\alpha_s}\int^\infty_0\frac{dr}{r}J_0(r k) e^{-S(r,\mu^2)} \sdpa(x,r),
	\label{eq:ww-sud}
\end{equation}
where, we use the Sudakov form factor~\cite{Mueller:2013wwa,Xiao:2017yya},
\begin{equation}
	S(r,\mu^2)=\frac{\alpha_s N_c}{4\pi}\ln^2\left(\frac{\mu^2r^2}{4e^{-2\gamma_E}}\right),
\end{equation}
in which $\gamma_E$ is the Euler-Mascheroni constant, and we use $\alpha_s=0.2$.

The present study is carried out in the framework of small-$x$-Improved Transverse-Momentum-Dependent (ITMD) factorization~\cite{Kotko:2015ura,vanHameren:2016ftb}.
ITMD factorization is implemented in the program KaTie~\cite{vanHameren:2016kkz}, which we will use to compute the cross section. 
ITMD is an generalization of TMD where the momentum imbalance is restricted to be small~\cite{Kotko:2015ura,vanHameren:2016ftb}. That is to say ITMD resums $(Q_s/k_T)^n$ and $(k_T/P_T)^n$, where $P_t\sim p_{1T},p_{2T}$ of jets~\cite{Kotko:2015ura,vanHameren:2016ftb}, thus extends the region of applicability up to $k_T\sim P_T$.

>>>>

\begin{abstract}
We investigate effects of exact gluon kinematics on the parameters of the
Golec-Biernat--W\"usthoff, and Bartels--Golec-Biernat--Kowalski models. The
resulting parameters show sizable difference, particularly in the normalization
$\sigma_0$. The resulting models are applied for the dijet process in DIS to
investigate effects of the Sudakov form factor.  The result qualitatively agrees
with that of Ref.~\cite{vanHameren:2021sqc}, except for the difference stemming
from the large-$k_T$ behaviour of the models.
\end{abstract}

@@

  \draw[ snake=coil,segment aspect=1.5,segment length=0.1in](0.5in , -1in)--(0.5in,-0.5in);
  \draw[snake=coil,segment aspect=1.5,segment length=0.1in](-0.5in , -1in)--(-0.5in,-0.5in);
\end{tikzpicture}
}
\caption{Kinematic variables of the gluon contribution to $F_2$. The momentum fraction of gluon is $x/z$ as it has to contribute via the quark box.
}
\label{fig:gluon-kinem}
\end{figure}
Factorization has played central role in QCD, where long-distance effects can be isolated into an object called parton distribution functions (PDFs)~\cite{roberts_1990,collins_2011}. 
The PDFs are not perturbatively calculable but they are process independent~\cite{collins_2011}. That is to say, that one needs to measure them in experiments, but the PDFs obtained one experiment can be used as input in another. A type of experiments called deep inelastic scattering~(DIS), has been one of experiments which largely contributed to the study of the structure of the proton~\cite{roberts_1990,collins_2011}. 
The election-ion collider (EIC)~\cite{NAP25171}, which is currently under construction, will be the next generation of the DIS experiments and expected to uncover more details about the structure.  
As one increases the center of mass energy at a fixed value of the photon virtuality, $Q$, one is probing the region of the small Bjorken scaling variable, $x$.
In the small-$x$ region of DIS process   
\begin{equation}
  %\label{eq:}
  e\, p\rightarrow \gamma^* (q)\, p(p)\rightarrow X\,,
\end{equation}
%
where are $p$ and $q$ are, respectively, the momenta of the photon and the
proton, the interactions are dominated by gluons\cite{Kovchegov:2012mbw}. As a photon does not interact directly with a gluon, it interact through a box of quarks as depicted in Fig.~\ref{fig:gluon-kinem}. 
An object, which is central to the description of this process is called dipole gluon density, $\mathcal{F}(x,k_T^2)$, which is a type of transverse momentum dependent PDFs (TMD PDF)~\cite{Dominguez:2010xd,Dominguez:2011wm,Xiao:2017yya}. This appears in the $k_T$-factorization formula~\cite{Dominguez:2010xd,Dominguez:2011wm,Xiao:2017yya}, which we will discuss later, and plays role similar to that of collinear parton distribution function in the collinear factorization.
The dipole gluon density is also called unintegrated gluon density~(UGD) since it is related to the collinear (integrated) gluon density by
\begin{equation}
xg(x,Q^2)=\int^{Q^2}_0 dk_T^2 \mathcal{F}(x,k^2_t).
\end{equation}
Much effort has been made to study this object, notably the work of Balistky, Fadin, Kuraev and Lipatov (BFKL)~\cite{Balitsky:1978ic, Kuraev:1977fs} has predicted sharp rise of cross sections with $1/x$.  However, such rise violates unitarity and the Froissart bound~\cite{Kovchegov:2012mbw,Barone:1993sy}. The work of Balitsky and Kovchegov (BK)~\cite{Balitsky:1995ub,Kovchegov:1999yj} incorporated the gluon recombination, by including nonlinear term in the evolution, thus taming the growth. The phenomenon described by this nonlinear term is called saturation. The meaning of the Froissart bound is that, asymptotically, the cross section can not grow faster than the size of black-disk (proton with high gluon density) which expands like $\ln(s)$~\cite{Badelek:1992gs}.
Despite the success of such evolution equations, there are several popular phenomenological models owing to their simplicity.

\sout{\comment{Some more general talk like in the previous paper}}

\sout{\comment{EIC}}

@@

Additionally, let us introduce $q'\equiv q+x p$. 
Then, one  decomposes $k$ and $\kappa$ (Fig.~\ref{fig:gluon-kinem}) as
\begin{align}
    \kappa&=\alpha p-\beta q'+\kappa_t&&\mathrm{and}& k&=a p- bq'+k_T.
\end{align}
For the contribution depicted in Fig.~\ref{fig:gluon-kinem}, the structure function, $F_2$ for transversely and longitudinally polarized photons, factorize, with a change of variable  ${\boldsymbol{\kappa}'}_t\equiv{\boldsymbol{\kappa}_t}-(1-\beta)\mathbf{k}_t$, in the form~\cite{ Kimber:2001uaa,Kwiecinski:1997ee}
\begin{multline}
	F_2(x,Q^2)=\sum_f e_f^2 \frac{Q^2}{2\pi}\int\frac{dk^2_t}{k_T^2}\int^1_0d\beta\int d{\kappa'}_t\alpha_s(\mu^2) \mathcal{F}(x/z,k_T^2)\Theta(1-x/z)\\
	\left[\left(\beta^2+(1-\beta)^2\right)\left(\frac{I_1}{2\pi}-\frac{I_2}{2\pi}\right)
	+\left(m_f^2+4Q^2\beta^2(1-\beta)^2\right)\left(\frac{I_3}{2\pi}-\frac{I_4}{2\pi}\right)\right],
	\label{eq:angle-integrated}
\end{multline}
where
\begin{equation}
	\frac{1}{z}=1+\frac{{\kappa'}^2_t+m_f^2}{\beta(1-\beta)Q^2}+\frac{k^2_t}{Q^2}.
	\label{eq:z}
\end{equation}
(see Ref.~\cite{ Kimber:2001uaa,Kwiecinski:1997ee} for detail.)
%and
%\begin{equation}
%	\begin{split}
%		\frac{I_1}{2\pi}=\frac{N_1N_2+N_3^2}{\left( N^2_1+2N_1N_2+N_3^2\right)^{3/2}}, &\hspace{1cm}
%		\frac{I_2}{2\pi}=\frac{N_3-(1-2\beta)N_1}{(N_1+N_4)\sqrt{ N^2_1+2N_1N_2+N_3^2}},\\
%		\frac{I_3}{2\pi}=\frac{N_1+N_2}{\left( N^2_1+2N_1N_2+N_3^2\right)^{3/2}},&\hspace{1cm}
%		\frac{I_2}{2\pi}=\frac{(1-\beta)}{(N_1+N_4)\sqrt{ N^2_1+2N_1N_2+N_3^2}},
%	\end{split}
%\end{equation}
%for
%\begin{equation}
%	\begin{split}
%		N_1\equiv\beta(1-\beta)Q^2+m_f^2, &\hspace{2cm}
%		N_2\equiv{\kappa'}_t^2+(1-\beta)^2k_T^2,\\
%		N_3\equiv{\kappa'}_t^2-(1-\beta)^2k_T^2, &\hspace{2cm}
%		N_4\equiv{\kappa'}_t^2+\beta(1-\beta)k_T^2.
%	\end{split}
%\end{equation}
%Hereafter, we will call Eq.~(\ref{eq:angle-integrated}) $k_T$-factorizaton formula.
One should note, that gluons are not probed directly, thus the argument of the gluon density is $x/z$ rather than $x$.
If one, instead, uses $ 1/z=\left(1+4 m_f^2/Q^2\right)$ and assumes that $\mu$ is independent of $\kappa'$ and $k_T$, 
the above formula can be written in the impact parameter space~\cite{Golec-Biernat:1998zce,Nikolaev:1990ja} (i.e. dipole-factorizaton formula)
\begin{equation}
F_2\left(x,Q^2\right)\sim\int^1_0d\beta \int d^2\mathbf{r}\left|\Psi\left(\tilde{x},\beta,Q^2\right)\right|^2\sigma_{\mathrm{dipole}}\left(\tilde{x},r\right),
\label{eq:dipole-factorization}
\end{equation}
where the photon wave function, $\left|\Psi\left(x,\beta,Q^2\right)\right|^2$, describes splitting of the incoming photon into a $q\overline{q}$ pair with light-cone momenta fractions $\beta$ and $1-\beta$ respectively, and the dipole cross section, $\sigma_{\mathrm{dipole}}\left(x,r\right)$, describes the interaction of the colour dipole of the size $r$ with the proton. In Ref.~\cite{Golec-Biernat:1998zce}, $\tilde{x}=x(1+4m_f/Q^2)$ with nonzero vale of $m_f$ even for light flavours, which is necessary to partially substitute $k_T$ and ${\kappa'}_T$ in Eq~(\ref{eq:z}). \\

@@

The results of fits are summarized in Tab.~\ref{tab:table}. 
The fit quality of $k_T$-GBW is almost unchanged w.r.t. $r$-GBW, while the rc-$k_T$-GBW shows remarkable improvement, almost halving the $\chi^2$ value.
It was pointed out in Ref.~\cite{Albacete:2004gw,Albacete:2007yr,Albacete:2010sy} that in the BK evolution, the running coupling correction have considerable effects.

Another notable point is that, except for the normalization $\sigma_0$, the parameters are very similar, particularly those of rc-$k_T$-GBW are almost identical to those of $r$-GBW. 
While the GBW model remains almost unaffected, the BGK model seems to show slightly more change. The difference in $\sigma_0$ is similar to that of GBW model, and other parameters changed moderately.
\sout{\comment{Describet what's in the figuers...} }
In Fig.~\ref{fig:GBW-BGK}, the plots of the dipole cross section, the dipole gluon density and the saturation scale are shown for the GBW and BGK models are shown. The dipole cross section and the gluon density are both normalized by $\sigma_0$ in order to see the effects  of other parameters better,
and the saturation scale is defined as a ridge of the dipole gluon density on the $(x,k_T^2)$ plane.\\
One can see, in the plots on the left side, the effects of the changes (or rather no changes) in the parameters of the GBW model. The difference between the rc-$k_T$-GBW and $r$-GBW are negligible, while the $k_T$-GBW is slightly shifted, compared to others, by the change in $x_0$.\\
On th right side of Fig.~\ref{fig:GBW-BGK}, the same plots for the BGK model are shown.
Unlike in the GBW model, the connection between the differences shown in the plots and the differences in the parameters are not clear. Nevertheless, the difference is more prominent in the small-$x$ region.
Comparisons of the results with the $F_2$ data are shown in Figs.~\ref{fig:GBW-Grid} and~\ref{fig:BGK-Grid}.
In Fig.~\ref{fig:GBW-Grid}, the difference between $r$-GBW and $k_T$-GBW are not visible, while rc-$k_T$-GBW shows sizable difference from the others, particularly in the large-$Q^2$ region. 
Recalling that the parameters of rc-$k_T$-GBW and $r$-GBW are very similar, the difference in $F_2$ is almost entirely due to the coupling constant. The improvement in the fit quality is depicted as a histogram of the $\chi^2$-vale per number of points at the bottom of Fig.~\ref{fig:GBW-Grid}. Here, the improvement in the large-$Q^2$ region is very clear.
In Fig.~\ref{fig:BGK-Grid}, the difference between $r$-BGK and $k_T$-BGK are hardly visible. In the histogram at the bottom, one can see some differences, but they cancel out mostly, making little improvement overall.

\begin{figure}[p]

  \begin{multicols}{2}
  \begin{subfigure}{0.5\textwidth}
    \includegraphics[width=\textwidth]{./plots/GBW-dipole.pdf}
    \includegraphics[width=\textwidth]{./plots/GBW-gluon.pdf}
    \includegraphics[width=\textwidth]{./plots/GBW-saturation.pdf}
    \caption{GBW}
    \label{fig:GBW}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
    \includegraphics[width=\textwidth]{./plots/BGK-dipole.pdf}
    \includegraphics[width=\textwidth]{./plots/BGK-gluon.pdf}
    \includegraphics[width=\textwidth]{./plots/BGK-saturation.pdf}
    \caption{BGK}
    \label{fig:BGK}
\end{subfigure}
  \end{multicols}
  \caption{The dipole cross section, the dipole gluon density at $x=10^{-2},\;
  10^{-6}$, and the saturation scale for the GBW (left) and the BGK (right)
  models. Note, the dipole cross section and the gluon density are normalized by
  $\sigma_0^{-1}$. \sout{\comment{Larger y and x labels}}} 
\label{fig:GBW-BGK}
\end{figure}

@@

\begin{figure}[p]
%\begin{subfigure}{\textwidth}
\includegraphics[width=0.49\textwidth]{./plots/Figure_2-1.png}
\includegraphics[width=0.49\textwidth]{./plots/Figure_2-2.png}
\includegraphics[width=\textwidth]{./plots/Figure_2-3.png}
%\end{subfigure}
\caption{Comparison of BGK $F_2$ with HERA data. The histogram shows the $\chi^2$ value per data point in each frame. While the overall fit quality remain similar, the fit quality in each frame change noticeably. Particularly the $k_T$-formula case ($k_T$) shows better fit in the small-$Q^2$ region.}
\label{fig:BGK-Grid}
\end{figure}
For the rest of this section, let us have a closer look at $\sigma_0$. 
Recalling that the difference between the $k_T$-factorization formula and the dipole-factorization formula is in $x/z$, where this enters in the GBW formalism as modified $x$. It is easy to see that, as $x$ grows, the dipole cross section gets suppressed (Keeping in mind the suppression by the photon wave function in the large-$r$ region.). Such effect was discussed previously in Ref.~\cite{Kutak:2004ym} in the context of the BK equation. In fact, this suppression is the motivation given in Ref.~\cite{Golec-Biernat:1998zce} for such modification of $x$, so that in the small-$Q^2$ limit, the total cross section remains finite.    
Since 
\begin{equation}
\left(1+\frac{4 m_f^2}{Q^2}\right)\leq\left(1+\frac{k_T^2}{Q^2}+\frac{{\kappa'}_t^2+m_f^2}{\beta(1-\beta)Q^2}\right),
\end{equation}
the $k_T$-factorization case receives more suppression. Consequently, the normalization factor $\sigma_0$ rises to compensate the suppression. 
Therefore, one can understand the change in $\sigma_0$ as a direct consequence of the key difference between the $k_t$-factorization and the dipole-factorization.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\section{Dijet process at EIC}
\label{Dijet process at EIC}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In order to investigate less inclusive processes, we will study the electron-dijet correlation at the electron-ion collider(EIC), following closely the method of Ref.~\cite{vanHameren:2021sqc}. 
At the leading order, the dijet DIS in small-$x$ limit is dominated by $q\overline{q}$ jets~\cite{}.
This process is therefore closely related to the dipole picture we discussed earlier (see. Ref.~\cite{Dominguez:2011wm}). In the Breit frame where the photon momentum is $q=(0,0,0,Q)$, at the leading order, the jets momentum imbalance $p_T\equiv\left|p_{1T}+p_{2T}\right|$ equals the gluon momentum $k_T$, where $p_{1T}$ and $p_{2T}$ are transverse momenta of the jets.
This makes dijets an interesting observable. For the region where $p_T\ll P_T\sim p_{1T},\,p_{2T}$, one may use power counting to take leading order in $p_T/P_T$, which leads to the transverse-momentum-dependent~(TMD) factorization .

\sout{\comment{process}}

\sout{\comment{factorization formula for dijets in DIS involving WW gluon}}

\sout{\comment{mention why Sudakov is important for dijet production}}

In the large-$N_c$ limit of the TMD factorization, there are two types of gluon densities, namely the dipole gluon density and the Weizs\"acker-Williams (WW) gluon density~\cite{Dominguez:2010xd,Dominguez:2011wm,vanHameren:2016ftb,Xiao:2017ggh}.  
It was shown in Ref.~\cite{Dominguez:2011wm}, that the dijet process in DIS can directly probe the WW gluon,$\fww(x,k^2)$, where the differential cross section factorizes as
\begin{equation}
	\frac{d\sigma^{\gamma^*p\rightarrow q\overline{q}X}}{d \mathrm{P.S.}}=\fww(x,k_T^2)H_{\gamma^*g\rightarrow q\overline{q}},
\end{equation}
with the hard function $H_{\gamma^*g\rightarrow q\overline{q}}$ describing interactions of an off-shell photon with an on-shell gluon to a $q\overline{q}$ pair.
$\fww(x,k^2)$, has an interpretation as a number density of gluons inside a proton, while $\fdp(x,k_T^2)$ does not have such an interpretation~\cite{Dominguez:2010xd,Dominguez:2011wm,Xiao:2017ggh}.

Under the Gaussian approximation and assuming $\theta$-like profile of the proton, one can write~\cite{vanHameren:2016ftb,Xiao:2017ggh,Dominguez:2010xd,Dominguez:2011wm}
\begin{equation}
\fww(x,k^2)= \frac{C_F}{2\pi^3\alpha_s}\int^\infty_0\frac{dr}{r}J_0(r k) \sdpa(x,r),
\end{equation} 	
with the adjoint dipole cross section
\begin{equation}
\sdpa(x,r)=\sigma_0\left( 1-\left(1-\frac{\sdp(x,r)}{\sigma_0}\right)^{C_A/C_F}\right).
\label{eq:ww}
\end{equation}

For the region where TMD factorization is applicable, $Q_s\sim k_T\ll P_T\sim Q$, one needs to resum the large Sudakov logarithms $\log(k_T/Q)$, as well as $\log(1/x)$~\cite{Dominguez:2011wm}. 
It was shown in Refs.~\cite{Mueller:2012uf,Mueller:2013wwa,Xiao:2017yya} that consistent resummation such logarithms are possible owing to the separation of corresponding regions.  
Resummation of the Sudakov logarithms is achieved by the formula~\cite{Mueller:2012uf,Mueller:2013wwa,Xiao:2017yya}
\begin{equation}
	\fww(x,k^2,\mu^2)= \frac{C_F}{2\pi^3\alpha_s}\int^\infty_0\frac{dr}{r}J_0(r k) e^{-S(r,\mu^2)} \sdpa(x,r),
	\label{eq:ww-sud}
\end{equation}
where, we use the Sudakov form factor~\cite{Mueller:2013wwa,Xiao:2017yya},
\begin{equation}
	S(r,\mu^2)=\frac{\alpha_s N_c}{4\pi}\ln^2\left(\frac{\mu^2r^2}{4e^{-2\gamma_E}}\right),
\end{equation}
in which $\gamma_E$ is the Euler-Mascheroni constant, and we use $\alpha_s=0.2$.

The present study is carried out in the framework of small-$x$-Improved Transverse-Momentum-Dependent (ITMD) factorization~\cite{Kotko:2015ura,vanHameren:2016ftb}.
ITMD factorization is implemented in the program KaTie~\cite{vanHameren:2016kkz}, which we will use to compute the cross section. 
ITMD is an generalization of TMD where the momentum imbalance in TMD is restricted to be small~\cite{Kotko:2015ura,vanHameren:2016ftb}. That is to say ITMD resums $(Q_s/k_T)^n$ and $(k_T/P_T)^n$~\cite{Kotko:2015ura,vanHameren:2016ftb}, thus extends the region of applicability up to $k_T\sim P_T$.
